Partitioning growth-dependent from growth-independent influences on tropical tree mortality

### 2018-08-19 ms/manuscript.Rnw
Correctly attribute figure panel
Incorporating Rick's comments

\affil[a]{Department of Biological Sciences, Macquarie University, Sydney, New South Wales, Australia}
\affil[b]{Field Museum of Natural History and Morton Arboretum, Chicago, Illinois, USA}
\affil[c]{Data61, CSIRO, Australia}
\affil[d]{Smithsonian Tropical Research Institute, Apartado 0843–03092, Balboa, Panama}
\affil[e]{Evolution and Ecology Research Centre, School of Biological, Earth and Environmental Science, University of New South Wales, Sydney, New South Wales, Australia}

@@

Data deposition: Code reproducing the results in this paper is available at \href{https://github.com/traitecoevo/mortality_bci}{github.com/traitecoevo/mortality\_bci}. Data from BCI is available at DOIs \href{http://doi.org/10.5479/data.bci.20130603.}{10.5479/data.bci.20130603.}, \href{http://doi.org/10.5479/data.bci20140711}{10.5479/data.bci20140711}.
}

@@

\begin{figure}[h!]
\includegraphics{figures/fig4.pdf}
\caption{Predicted changes in annual mortality probability with increasing growth rate. A) Estimated average curves for all 203 Barro Colorado Island species used in this study. B,C,D) represent average ($\pm$ 95\% credible intervals) curve for a high (red) and low (blue) trait values. B) wood density values 0.2 vs 0.8 (g cm$^{-3}$); C) maximum dbh values 3 vs 180 cm; D) light demand values 0.5 vs 0.8. Note that the intercept is the sum of $\alpha$ and $\gamma$ (i.e. the stochastic chance of death plus effect of low growth. Species with highest asymptote was \textit{Palicourea guianensis} where \Sexpr{subset(death_proportion(x), species =="Palicourea guianensis")[["n_deaths"]]} out of \Sexpr{subset(death_proportion(x), species =="Palicourea guianensis")[["n_total"]]} individuals died between 1995 and 2010.}
\label{fig4}
\end{figure}

@@

\acknow{We thank H. Muller-Landau and anonymous reviewers for feedback and B. Carpenter for technical advice. We acknowledge S. Hubbell, R. Foster, R. Pérez, S. Aguilar, S. Lao, S. Dolins, \& hundreds of field workers for their contribution; and the National Science Foundation, Smithsonian Tropical Research Institute, \& MacArthur Foundation for funding the design, collection, quality control and management of long-term growth data at BCI. Fig. 1a uses images by Tracey Saxby, IAN Image Library. J.S.C., R.G.F., L.M. and D.S. were supported by the Science and Industry Endowment Fund (SIEF; RP04-174). D.S.F. and M.W. were supported by fellowships from the Australian Research Council.}

>>>>

\affil[a]{Department of Biological Sciences, Macquarie University, Sydney, New South Wales, Australia}
\affil[b]{Field Museum of Natural History, Chicago, IL, USA and Morton Arboretum, Lisle, IL, USA}
\affil[c]{Data61, CSIRO, Australia}
\affil[d]{Smithsonian Tropical Research Institute, Apartado 0843–03092, Balboa, Panama}
\affil[e]{Evolution and Ecology Research Centre, School of Biological, Earth and Environmental Science, University of New South Wales, Sydney, New South Wales, Australia}

@@

Data deposition: Code reproducing the results in this paper is available at \href{https://github.com/traitecoevo/mortality_bci}{github.com/traitecoevo/mortality\_bci}. Data from BCI is available at DOIs \href{http://doi.org/10.5479/data.bci.20130603}{10.5479/data.bci.20130603}, \href{http://doi.org/10.5479/data.bci20140711}{10.5479/data.bci20140711}.
}

@@

\begin{figure}[h!]
\includegraphics{figures/fig4.pdf}
\caption{Predicted changes in annual mortality probability with increasing growth rate. A) Estimated average curves for all 203 Barro Colorado Island species used in this study. B,C,D) represent average ($\pm$ 95\% credible intervals) curve for a high (red) and low (blue) trait values. B) wood density values 0.2 vs 0.8 (g cm$^{-3}$); C) maximum dbh values 3 vs 180 cm; D) light demand values 0.5 vs 0.8. Note that the intercept is the sum of $\alpha$ and $\gamma$ (i.e. the stochastic chance of death plus effect of low growth. Species with highest asymptote was \textit{Palicourea guianensis} where \Sexpr{subset(death_proportion(BCI_training_full), species =="Palicourea guianensis")[["n_deaths"]]} out of \Sexpr{subset(death_proportion(BCI_training_full), species =="Palicourea guianensis")[["n_total"]]} individuals died between 1995 and 2010.}
\label{fig4}
\end{figure}

@@

\acknow{We thank H. Muller-Landau and anonymous reviewers for feedback and B. Carpenter for technical advice. We acknowledge S. Hubbell, R. Foster, R. Pérez, S. Aguilar, S. Lao, S. Dolins, \& hundreds of field workers for their contribution; and the National Science Foundation, Smithsonian Tropical Research Institute, \& MacArthur Foundation for funding the design, collection, quality control and management of long-term growth data at BCI. Fig. 1b uses images by Tracey Saxby, IAN Image Library. J.S.C., R.G.F., L.M. and D.S. were supported by the Science and Industry Endowment Fund (SIEF; RP04-174). D.S.F. and M.W. were supported by fellowships from the Australian Research Council.}

### 2018-08-19 ms/supplementary.Rnw
Minor typos
Incorporating Rick's comments

\title{Unifying intra- and inter-specific variation in tropical tree mortality}
\author{J.S. Camac, R. Condit, R.G. FitzJohn, L. McCalman, D. Steinberg, M. Westoby, S.J. Wright, D.S. Falster}
\correspondingauthor{Corresponding James S Camac. E-mail: james.camac@gmail.com}

@@

The other way survival models may differ is in how the predicted survival curve responds to covariates. Both the hazard rate and survival models predict a relationship between covariates and the probability of death across a specified time period. In the main text, we argue that biologically, it makes sense for this probability to asymptote above zero. Yet, aside form the additive hazards model we present, the other methods that we have encountered will all drive probability of death to zero when growth rate is high (assuming growth rate is included as a covariate). In other words, the models behave like the centre panel in Fig 1b.

>>>>

\title{Partitioning growth-dependent from growth-independent influences on tropical tree mortality}
\author{J.S. Camac, R. Condit, R.G. FitzJohn, L. McCalman, D. Steinberg, M. Westoby, S.J. Wright, D.S. Falster}
\correspondingauthor{Corresponding James S Camac. E-mail: james.camac@gmail.com}

@@

The other way survival models may differ is in how the predicted survival curve responds to covariates. Both the hazard rate and survival models predict a relationship between covariates and the probability of death across a specified time period. In the main text, we argue that biologically, it makes sense for this probability to asymptote above zero. Yet, aside form the additive hazards model we present, the other methods that we have encountered will all drive probability of death to zero when growth rate is high (assuming growth rate is included as a covariate). In other words, the models behave like the centre panel in Fig 1a.
